Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

This example has been used as a real-world testbed driving our experimental implementation.
%
For the sake of brevity,
we do not report the entire configuration in this manuscript, but it is available in the companion artifact~\cite{https://doi.org/10.5281/zenodo.7933160}
% \meta{
%     NICOLAS please replace TBD with the artifact citation from zenodo. Use doi2bib to get the bibtex entry.
% }
for those willing to exercise the whole system.
%
To simplify testing we also provide,
in the same artifact,
a simulation of the system where every device is containerised.

>>>>

This example has been used as a real-world testbed driving our experimental implementation.
%
For brevity,
we do not report the entire configuration in this manuscript, but it is available in the companion artifact~\cite{https://doi.org/10.5281/zenodo.7933160}
% \meta{
%     NICOLAS please replace TBD with the artifact citation from zenodo. Use doi2bib to get the bibtex entry.
% }
for those willing to exercise the whole system.
%
To simplify testing we also provide,
in the same artifact,
a simulation of the system where every device is containerised.
